---
title: "FRST 507C Project Update: Data Simulation"
author: "Adam Fong"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(ggplot2)
source("../bayesian/simulation_delta_h_all.R")
source("../viz/hardiness_delta_tmean.R")
source("../viz/hardiness_plot_all.R")
```

## Overview
- How does air temperature effect how grapevines accumulate cold hardiness? 

- Hardiness is measured as the lowest air temperature that does not result in grapevine death (LTE50)

## Hardiness in Dormancy
``` {r }
suppressWarnings(print(hardiness_phases))
```

## Change in Hardiness in Dormancy
```{r hardiness_delta_tmean}
suppressWarnings(print(hardiness_delta_tmean))
```


## Simulated Data
```{r true_params}
suppressWarnings(print(true_params))

```


## Fitting stan_glm with Interactions
```{r}
fit
```

## Simulation Parameter Recovery
| **Parameter** | **Value** | **Recovery From Fit** |
| :---------: | :--------: | :------: |
| Intercept (all phases) | 0 | 0.1 |
| Cold Acclimation Beta | -0.33 | -0.3 |
| Deep Dormancy Beta | -0.02 | 0.0 |
| Deacclimation Beta | 0.33 | 0.4 | 


## Simulation with 100 Posterior Draws
```{r }
posterior_preds
```

## Next Steps

- Account for variety / site in model
- Use a cumulative weather metric such as chilling degree days as a predictor
- Make phase boundaries calculated from temperature instead of visual approximation
- Define weakly informed priors


